Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-02 paper/manuscript.tex
Some more progress on last results section

However, to quantify the extent of mutational shifts at a site-by-site level, we used an approach described in \comment{haddox2017}.
We aligned Perth/2009 H3 and WSN/1933 H1 and at each alignable site calculated the difference in preferences between homologs while correcting for experimental noise within homologs.
The distribution of shifts is shown in Figure~\ref{fig:distance_distribution}C.

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/RMSD_heatmap/RMSD_heatmap.pdf}}
\caption{\label{fig:RMSD_heatmap}
{\bf Shifts in preferences mapped onto the structure of HA}
(A) The preference shifts as calculated by $RMSD_{corrected}$ between the two HA homologs is mapped onto the structure of HA (PDB 4O5N, citation). 
The left structure shows the HA trimer, and the right structure colors one of the monomers. 
The sialic acid receptor is shown in black sticks.
Gray indicates little shifts in preference, while red indicates large shifts in preference.
The top ten most shifted sites are shown in spheres on the monomer.
(B)
}
\end{figure}

>>>>

However, to quantify the extent of mutational shifts at a site-by-site level, we used an approach described in \comment{haddox2017}.
We aligned Perth/2009 H3 and WSN/1933 H1 and at each alignable site calculated the difference in preferences between homologs while correcting for experimental noise within homologs.
The distribution of shifts is shown in Figure~\ref{fig:distance_distribution}C.
Although many sites have small shifts near zero, a considerable number of sites have large shifts in preference, reaching a difference of 0.86 out of a maximum possible of 1.0.
When we compare HA to the preferences measured in the non-homologous protein HIV Env \comment{haddox2017}, nearly all sites are shifted.
On the other hand, when we randomize the HA replicates to generate a null distribution, there is very little shift in preferences. 
For comparison, the preferences of the HIV Env homologs, which are 86\% identical at the amino-acid level, are mostly similar. 
Although there are a small number of sites with larger shifts reaching a maximum of 0.52, we do not see a dramatic tail in the distribution as we see for the HA's.
These observations suggest that as homologs diverge, their preferences increasingly shift.

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/RMSD_heatmap/RMSD_heatmap.pdf}}
\caption{\label{fig:RMSD_heatmap}
{\bf Shifts in preferences mapped onto the structure of HA}
(A) The preference shifts as calculated by $RMSD_{corrected}$ between the two HA homologs is mapped onto the structure of HA (PDB 4O5N;~\cite{lee2014receptor}). 
The left structure shows the HA trimer, and the right structure colors one of the monomers. 
The sialic acid receptor is shown in black sticks.
Blue indicates small shifts in preference near zero, while red indicates large shifts in preference.
The top ten most shifted sites are shown in spheres on the monomer.
(B) The stalk domain was found to be significantly less shifted than the head domain (left plot).
Sites absolutely conserved all 18 HA subtypes were also found to be significantly less shifted than the remaining non-conserved sites (right plot).
(C) 
}
\end{figure}
